G2G: Graph to Graph Mapping Framework for Interoperable Use of RDF and Property Graphs

### 2020-01-27 paper.tex
Change title
Updates from Overleaf

\begin{document}
\newtheorem{defi}[theorem]{Definition}
%
%\title{G2GML: Graph to Graph Mapping Language for Interoperable Use of RDF and Property Graphs}
\title{Graph to Graph Mapping Framework for Interoperable Use of RDF and Property Graphs}
%
\titlerunning{Graph to Graph Mapping Framework}
%\titlerunning{Interoperable Use of RDF and Property Graph}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Hirokazu Chiba\inst{1} \and Ryota Yamanaka\inst{2} \and Shota Matsumoto\inst{3}}
%
\authorrunning{H. Chiba {\itshape et al.}}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Database Center for Life Science, Chiba 277-0871, Japan\\
\email{chiba@dbcls.rois.ac.jp}
\and
Oracle Corporation, Bangkok 10500, Thailand\\
\email{ryota.yamanaka@oracle.com}
\and
Lifematics Inc., Tokyo 101-0041, Japan\\
\email{shota.matsumoto@lifematics.co.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% The abstract should briefly summarize the contents of the paper in 15--250 words.
Increasing amounts of scientific and social data are described as graphs. In addition to the standardized Resource Description Framework (RDF) model, the property graph model has been attracting increasing attention in the context of graph analysis. 
However, interoperable management of such graph data is challenging due to the differences in existing models and formats depending on various implementations. Here, we redefine the property graph model incorporating the differences in existing models and propose exchangeable serialization formats for property graphs, which can be converted into specific formats for each of the databases. 
The serialization formats independent of certain database implementations will increase the interoperability of graph databases and will make it easier for users to import accumulated graph data.
We further propose a framework for mapping RDF graphs to property graphs on the basis of the Graph to Graph Mapping Language (G2GML). Using this framework, accumulated graph data described in RDF can be converted to property graphs, which can then be loaded into several graph database engines for further analysis. 
%This work provides interoperability not only between property graph formats but also between RDF and proper graphs.
%Future works include implementing and utilizing graph algorithms to make the most of the accumulated data in various analytical engines.

@@

Here, we redefine the property graph model incorporating the differences in existing models and also propose serialization formats based on the data model. We further propose a graph to graph mapping framework on the basis of the Graph to Graph Mapping Language (G2GML). Using this mapping framework, accumulated graph data described in RDF can be converted into property graphs, which can then be loaded into several graph database engines for further analysis.

\section{The Property Graph Model}
Here we define the property graph model independent of specific graph database implementations. For the purpose of interoperability, we incorporate differences in property graph models, taking into consideration multiple labels or property values for nodes and edges, as well as mixed graphs with both of directed and undirected edges. The property graph model we redefine here requires the following characteristics:

@@

\section{Serializing Property Graphs}
According to our definition of the property graph model, we propose serialization in flat text and JSON. The flat text format (PG) is better for human readability and line-oriented processing, while the JSON format (JSON-PG) is best used for server-client communication.

@@

\section{Mapping RDF Graphs to Property Graphs}

@@

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{dataflow.png}
\caption{Overview of the graph to graph mapping}
\label{fig:dataflow}
\end{figure}

@@

\section{Discussion}
Recently, the graph data have been attracting increasing attention, leading to plethora of database implementations. 
%So far, there have been implementations of graph databases on the basis of various data models and query languages. 
%So far, there are differences in data models and query languages based on the implementations of graph databases.
So far, there have been different data models and query languages for these graph database implementations.
Thus, there have been community-based activities for standardizing graph query language for interoperable use of property graph databases~\cite{angles3}. Similarly, standardization of the property graph model of various database implementations will enhance the interoperable use of graph data. In fact, there is a need for graph standardization in the community and graph data standardization was recently discussed in a W3C workshop~\cite{w3c}; there were similar proposals for property graph model and serialization~\cite{tomaszuk} including ours and it is noteworthy that the two independent approaches have converged to the similar solution. 
In particular, our serialization has implementation for some of the major database engines and also has a potential to cover further various implementations. %However, it requires developing a converter for each format. 
%This work provides a basis of an interoperable platform for creating, exchanging, and utilizing property graph data.
%Specifically, our model and serialization are independent of specific implementations and provides a basis 
%Specifically, it provides the basis for mapping of our G2GML mapping. 
The serialization formats independent of certain database implementations will increase the interoperability of graph databases and will make it easier for users to import accumulated graph data.
%In G2G mapping, PG format works as a gateway from RDF to property graphs.

@@

@@

%\bibitem{sparql}
%SPARQL 1.1 Query Language, W3C Recommendation 21 March 2013. \url{http://www.w3.org/TR/sparql11-query/}

@@

>>>>

\begin{document}
\newtheorem{defi}[theorem]{Definition}
%
\title{G2G: Graph to Graph Mapping Framework for Interoperable Use of RDF and Property Graphs}
%
\titlerunning{G2G: Graph to Graph Mapping Framework}
%\titlerunning{Interoperable Use of RDF and Property Graph}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Hirokazu Chiba\inst{1} \and Ryota Yamanaka\inst{2} \and Shota Matsumoto\inst{3}}
%
\authorrunning{H. Chiba {\itshape et al.}}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Database Center for Life Science, Chiba 277-0871, Japan\\
\email{chiba@dbcls.rois.ac.jp}
\and
Oracle Corporation, Bangkok 10500, Thailand\\
\email{ryota.yamanaka@oracle.com}
\and
Lifematics Inc., Tokyo 101-0041, Japan\\
\email{shota.matsumoto@lifematics.co.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% The abstract should briefly summarize the contents of the paper in 15--250 words.
Increasing amounts of scientific and social data are described as graphs. In addition to the standardized Resource Description Framework (RDF) model, the property graph model has been attracting increasing attention in the context of graph analysis. 
However, interoperable management of such graph data is challenging due to the differences in existing models and formats depending on various implementations. Here, we redefine the property graph model incorporating the differences in existing models and propose exchangeable serialization formats for property graphs, which can be converted into specific formats for each of the databases. 
The serialization formats independent of certain database implementations will increase the interoperability of graph databases and will make it easier for users to import accumulated graph data.
We further propose a framework for mapping RDF graphs to property graphs on the basis of the Graph to Graph Mapping Language (G2GML). Using this framework, accumulated graph data described in RDF can be converted to property graphs, which can then be loaded into several graph database engines for further analysis. 
%This work provides interoperability not only between property graph formats but also between RDF and proper graphs.
%Future works include implementing and utilizing graph algorithms to make the most of the accumulated data in various analytical engines.

@@

Here, we redefine the property graph model incorporating the differences in existing models and also propose serialization formats based on the data model. We further propose a graph to graph mapping framework on the basis of the Graph to Graph Mapping Language (G2GML). Using this mapping framework, accumulated graph data described in RDF can be converted into property graphs, which can then be loaded into several graph database engines for further analysis. We will show several use cases where publicly available RDF data is extracted and convert to property graphs and also evaluate the performance. This work provides the foundation of interoperability of knowledge graphs.

The contribution of this paper is 1) development of Graph to Graph Mapping Lauguage 2) proposal of common propergy graph model and serialization 3) development of G2G mapper 4) construction of knowledge graph resources in a common format as Graph Archive.

%%%%%%%%%%%%%%%%%%%%%%%
\section{G2G Framework}

\subsection{Overview}

Here we illustrate the overview of the framework.
G2G is framework to describe mapping between RDF and property graphs for interoperable use of them. In this framework, users can specify mappings from RDF to property graphs in G2GML.
This mapping is processed by a tool called G2G Mapper, which was implemented by authors (available on \url{https://github.com/g2glab/g2g}). This tool can convert RDF data retrieved from SPARQL endpoints or from local files into PG format and then into specific formats for each of the database implementations.

As an entry point to property graph, we define the Property Graph format, which is based on the Property Graph model.

%%%%%%%%%%%%%%%%%%
\subsection{G2GML}

G2GML is a declative laugage, where patterns of RDF and property graphs are described. RDF pattern is described using SPARQL pattern, and property graph pattern is described using Cypher pattern.

\subsubsection{Preliminaries}

An RDF triple $(s, p, o)$ is an element of $(I \cup B) \times I \times (I \cup B \cup L)$ where $I$, $L$ and $B$ are a set of IRIs, a set of literals and a set of blank nodes, which are considered pairwise disjoint. In this paper, an RDF triple is simply called a triple. For a triple $(s, p, o)$, $s$ is called the subject, $p$ the predicate and $o$ the object. An RDF graph is defined as a finite set of triples.

\subsubsection{G2GML}
G2GML describes maps from RDF graphs to Property graphs.
RDF graph pattern yields solution sets of SPARQL, that is, variables and bindings.
Resultant nodes are generated by embedding bindings to its corresponding location.
Values bound in SPARQL solutions can be used only as labels or values of properties.

In this paper, we call maps written in G2GML as \textit{G2G maps}.
A \textit{G2G map} consists of one or more \textit{node maps} and \textit{edge maps}.
A \textit{node map} is a function that maps from an RDF graph to a set of \textit{PG nodes}. 
An \textit{edge map} is a function that maps from an RDF graph to a set of \textit{PG edges}.

A node map can be described as a pair of (i) a template of a PG node and (ii) an RDF graph pattern that can be written as \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).

\begin{defi}[PG node template]
%\leavevmode \vspace{1mm} \\
\emph{Syntax of PG node template.}
\begin{scriptsize}
\begin{verbatim}
<node_template> ::= "(" node_resource  ":" label  ("{" <property_list> "}")? ")"
<property_list> ::= <property> "," <property_list> | <property>
<property> ::= key":" value
\end{verbatim}
\end{scriptsize}
\end{defi}

A PG node template is interpreted as a map from a solution of SPARQL query to a tuple of a node, its label and its properties.  A variable bound to \texttt{node\_resource} is used as the primary key of the map. Other variables bound to \texttt{value} are concatenated into an array.

\begin{defi}[PG edge template]
%\leavevmode \vspace{1mm} \\
\emph{Syntax of PG edge template.}
\begin{scriptsize}
\begin{verbatim}
<edge_template> ::= "(" src_resource  ":" src_label ")" - "[" edge_resource?  ":" edge_label  ("{" 
<property_list> "}")? ")" (-> | -) "(" dst_resource  ":" dst_label ")"
\end{verbatim}
\end{scriptsize}
\end{defi}

%%%%%%%%%%%
\subsection{The Property Graph Model}
Here we define the property graph model independent of specific graph database implementations. For the purpose of interoperability, we incorporate differences in property graph models, taking into consideration multiple labels or property values for nodes and edges, as well as mixed graphs with both of directed and undirected edges. The property graph model we redefine here requires the following characteristics:

@@

\subsection{Serialization of Property Graphs}
According to our definition of the property graph model, we propose serialization in flat text and JSON. The flat text format (PG) is better for human readability and line-oriented processing, while the JSON format (JSON-PG) is best used for server-client communication.

@@

%%%%%%%%%%%%
\subsection{Minimal Exmples}
Figure~\ref{fig:example-g2g} shows the small example of G2G mapping from RDF data to PG data. This example shows the following five types of the typical mapping.

\begin{itemize}
    \item Resource to node: In the line 2-4, the RDF resources with type \texttt{:Person} are mapped into PG nodes using their URIs as node IDs.
    \item Datatype property to node property: In the line 2-4, the RDF datatype property \texttt{:name} is mapped into PG node property key \texttt{name}. The literal objects 'Alice' and 'Bob' are mapped into the node property values.
    \item Object property to edge: In the line 5-6, the RDF object property \texttt{:likes} is mapped into PG edge \texttt{follows}. 
    \item Resource to edge: In the line 7-10, the RDF resource with type \texttt{:Follow} is mapped into PG edge \texttt{follows}. 
    \item Datatype property to edge property: In the line 7-10, the RDF datatype property \texttt{:since} is mapped into PG edge property \texttt{since}. The literal objects \texttt{2017} is mapped into the edge property value.
\end{itemize}

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}
@prefix : <http://example.org/> .
:person1 a :Person ;
         :name 'Alice' .
:person2 a :Person ;
         :name 'Bob' .
:person1 :likes :person2 .
[] a :Follow ;
   :follower :person1 ;
   :followed :person2 ;
   :since 2017 .
\end{verbatim}
\end{scriptsize}
\caption{Example of input RDF data}
\label{fig:example-rdf}
\end{figure}

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}
PREFIX : <http://example.org/>
(p:Person {name:n})
    ?p a :Person .
    ?p :name ?n .
(p1:Person)-[:likes]->(p2:Person)
    ?p1 :likes ?p2 .
(p1:person)-[:follows {since:s}]->(p2:person)
    ?f :follower ?p1 ;
       :followed ?p2 ;
       :since ?s .
\end{verbatim}
\end{scriptsize}
\caption{Example of G2G mapping definition}
\label{fig:example-g2g}
\end{figure}

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}
"http://example.org/person1" :person name:Alice
"http://example.org/person2" :person name:Bob
"http://example.org/person1" -> "http://example.org/person2" :likes
"http://example.org/person1" -> "http://example.org/person2" :follows since:2017
\end{verbatim}
\end{scriptsize}
\caption{Example of output PG data}
\label{fig:example-pg}
\end{figure}

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{pg_example5.png}
\caption{Example of created PG}
\label{fig:pg_example5}
\end{figure}

%%%%%%%%%%%
\subsection{Mapping Details}
The G2G mapping based on G2GML is generally intuitive as it is shown above, however, there are several discussions about the details of mapping.

\subsubsection{Multi Edges}
When there are multiple information of potential edges between the same pair of resources in RDF.

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}
@prefix : <http://example.org/> .
:person1 a :Person ;
         :name 'Alice' .
:person2 a :Person ;
         :name 'Bob' .
[] a :Follow ;
   :follower :person1 ;
   :followed :person2 ;
   :since 2017 .
[] a :Follow ;
   :follower :person1 ;
   :followed :person2 ;
   :since 2018 .
\end{verbatim}
\end{scriptsize}
\caption{Example of input RDF data (multi edges)}
\label{fig:example-rdf2}
\end{figure}

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}
"http://example.org/person1" :Person name:Alice
"http://example.org/person2" :Person name:Bob
"http://example.org/person1" -> "http://example.org/person2" :follows since:2017
"http://example.org/person1" -> "http://example.org/person2" :follows since:2018
\end{verbatim}
\end{scriptsize}
\caption{Example of output PG data (multi edges)}
\label{fig:example-pg2}
\end{figure}

\subsubsection{List of Property Values}
PG property can have multiple values. When the same data property is put multiple times on a resource, the values are assumed to be the members of a list.

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}

@prefix : <http://example.org/> .
:person1 a :Person ;
         :name 'Alice' ;
         :name 'Allie' .
:person2 a :Person ;
         :name 'Bob' .
[] a :Follow ;
   :follower :person1 ;
   :followed :person2 ;
   :since 2017 ;
   :since 2018 .

\end{verbatim}
\end{scriptsize}
\caption{Example of input RDF data (list of property values)}
\label{fig:example-rdf3}
\end{figure}

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}

"http://example.org/person1" :Person name:Alice name:Allie
"http://example.org/person2" :Person name:Bob
"http://example.org/person1" -> "http://example.org/person2" :follows since:2017 since:2018

\end{verbatim}
\end{scriptsize}
\caption{Example of output PG data (list of property values)}
\label{fig:example-pg3}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{G2G Mapper}

G2G mapper is implemented in JavaScript, and can be executed using Node.js in command line.

\texttt{g2g musician.g2g http://dbpedia.org/sparql}

\noindent where the first argument is G2GML mapping file and the second argument is target SPARQL endpoint from which to extract RDF data.

Also, demonstration cite of G2G mapper is available (Figure~\ref{fig:sandbox}).

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{sandbox.png}
\caption{G2G sandbox}
\label{fig:sandbox}
\end{figure}

%%%%%%%%%%%%%%%%%%%
\section{Use Cases}

We  present several use cases to show the usefulness of G2G mapping framework, where we use publicly available open data available in RDF through SPARQL endpoint.

Figure~\ref{fig:dataflow} shows the overview of the mapping.
In this framework, users can specify mappings from RDF to property graphs in G2GML.
This mapping is processed by a tool called G2G Mapper, which was implemented by authors (available on \url{https://github.com/g2glab/g2g}). This tool can convert RDF data retrieved from SPARQL endpoints or from local files into PG format and then into specific formats for each of the database implementations.

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{dataflow.png}
\caption{Overview of the mapping from RDF to property graph}
\label{fig:dataflow}
\end{figure}

\subsection{Using Wikidata}

Here we present use case of for Wikidata.
Wikidata is a useful source of biological open data, and it is available in the form of RDF through the SPARQL interface.

In Wikidata, each disease is associated with zero or more genes and drugs.
The subset of Wikidata can be extracted using G2G framework by writing a mapping file in G2GML (see the following list).
Here, we focus on human genes. So we specified the necessary conditions in G2GML.
Each entity of ‘Q12136: disease’ can have property ‘P2176: drug used for treatment’, thereby linked to items of ‘Q12140: medication’. Also, each disease can have property ‘P2293: genetic association’, thereby linked to items of ‘Q7186: gene’.

The numbers of obtained entities are as follows.

4689 diseases
4495 human genes
1285 drugs

The following figure shows the schematic relationships between those entities.

\begin{figure}
\center
\includegraphics[width=0.7\textwidth]{wikidata_schema.png}
\caption{Schematic relation of Wikidata entities}
\label{fig:wikidata_schema.png}
\end{figure}

\begin{figure}[!t]
\vspace{2mm}
\begin{scriptsize}
\begin{verbatim}

PREFIX wd: <http://www.wikidata.org/entity/>
PREFIX wdt: <http://www.wikidata.org/prop/direct/>

(g:HumanGene {symbol: s})
    ?g wdt:P31 wd:Q7187 ;      # instance of gene
       wdt:P703 wd:Q15978631 ; # found in taxon Homo sapiens
       wdt:P353 ?s .           # HGNC gene symbol

(d:Disease {name: n})
    ?d wdt:P31 wd:Q12136 ;     # instance of disease
       rdfs:label ?l .
    FILTER(lang(?l) = "en")
    BIND(str(?l) AS ?n)

(m:Drug {name: n})
    ?m wdt:P31 wd:Q12140 ;     # instance of medication
       rdfs:label ?l .
    FILTER(lang(?l) = "en")
    BIND(str(?l) AS ?n)

(d:Disease)-[:hasAssociatedGene]->(g:HumanGene)
    ?d wdt:P2293 ?g .          # genetic association

(d:Disease)-[:hasDrug]->(m:Drug)
    ?d wdt:P2176 ?m .          # drug used for treatment

\end{verbatim}
\end{scriptsize}
\caption{G2GML for Wikidata extraction}
\label{fig:g2gml_wikidata}
\end{figure}

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{neo4jexample2.png}
\caption{Visualization on Neo4j}
\label{fig:neo4jexample2.png}
\end{figure}

\subsection{Using DBpedia}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Evaluation}

% The goal of our evaluation is to observe the impact the number of the nodes and edges on the performance and
% analyzing its scalability when the size of the datset increases.
% \begin{itemize}
% \item Q1) : Is the runtime affected when more nodes are added?
% \item Q2) : Does it scale to a larger dataset?
% \item Q3) : How does it scale when adding a larger number of datasets?
% \end{itemize}

\subsubsection{Graph Archive}
We created several G2GML mappings to extract public RDF from endpoint and construct knowledge graphs in PG format and resulting knowledge graphs as Graph Archive.

In the listed knowledge graphs, we compared the number of nodes and edges between RDF and property graphs.

\section{Related Work}
Recently, the graph data have been attracting increasing attention, leading to plethora of database implementations. 
%So far, there have been implementations of graph databases on the basis of various data models and query languages. 
%So far, there are differences in data models and query languages based on the implementations of graph databases.
So far, there have been different data models and query languages for these graph database implementations.
Thus, there have been community-based activities for standardizing graph query language for interoperable use of property graph databases~\cite{angles3}. Similarly, standardization of the property graph model of various database implementations will enhance the interoperable use of graph data. In fact, there is a need for graph standardization in the community and graph data standardization was recently discussed in a W3C workshop~\cite{w3c}; there were similar proposals for property graph model and serialization~\cite{tomaszuk} including ours and it is noteworthy that the two independent approaches have converged to the similar solution. 
In particular, our serialization has implementation for some of the major database engines and also has a potential to cover further various implementations. %However, it requires developing a converter for each format. 
%This work provides a basis of an interoperable platform for creating, exchanging, and utilizing property graph data.
%Specifically, our model and serialization are independent of specific implementations and provides a basis 
%Specifically, it provides the basis for mapping of our G2GML mapping. 
The serialization formats independent of certain database implementations will increase the interoperability of graph databases and will make it easier for users to import accumulated graph data.
%In G2G mapping, PG format works as a gateway from RDF to property graphs.

@@

A previous work compared performance of Blazegraph and Neo4j. They concluded that RDF has advantage in terms of performance and interoperability.

@@

\bibitem{sparql}
SPARQL 1.1 Query Language, W3C Recommendation 21 March 2013. \url{http://www.w3.org/TR/sparql11-query/}

@@

\bibitem{Alocci}
Alocci, D., Mariethoz, J., Horlacher, O., Bolleman, J. T., Campbell, M. P., & Lisacek, F. (2015). Property graph vs RDF triple store: A comparison on glycan substructure search. PloS one, 10(12), e0144578.
